Технология использования открытых данных Федеральной налоговой службы России для экономико-географического анализа

### 2024-01-08 Paper.Rmd
Proofreading of English meta, title change

**Использование открытых данных налоговой службы для создания геопривязанного набора данных о субъектах малого и среднего предпринимательства в России**

>>>>

**Технология создания геопривязанного набора данных о субъектах малого и среднего предпринимательства в России на базе открытых данных налоговой службы**

### 2024-01-08 Paper_meta_en.Rmd
Proofreading of English meta, title change

**Technology of Using Federal Taxpayer Service's Open Data for Making a Geo-Referenced Dataset about Small and Medium-Sized Businesses in Russia**

@@

Syomin Pavel Olegovich: ntsp\@ya.ru, ORCID 0000-0002-4015-9206

@@

```{r tab-1-sizes-funnel}
bytes_in_mb <- 2 ** 20
sizes_funnel <-  sizes_funnel / bytes_in_mb
knitr::kable(
  sizes_funnel,
  digits = 0,
  format.args = list(scientific = FALSE),
  col.names = c("SMB Registry", "Revenue+Expediture", "Employees", "Total"),
  caption = "Table 1. Change in the data volumes during program execution (in megabytes). Rows are stages, columns are source datasets and totals")
```

@@

```{r fig-3-regions-agri-forest, fig.cap = "Fig. 3. Regional distribution of SMBs which main activity is agriculture or forestry. Color represents the min-max scaled value"}
regions_plot_agri_forestry
```

@@

```{r fig-3-regions-wheat-potato, fig.cap = "Fig. 4. Regional distribution of SMBs which main activity is growing of wheat or potato. Color represents the min-max scaled value, gray is no data"}
regions_plot_wheat_potato
```

@@

```{r fig-5-activity-by-settlements-russia, fig.cap = "Fig. 5. Count of SMBs in some Russian settlements with dominant activity type. The counts are represented with circle size, and the most popular activity group in the settlement is displayed by color. Only settlements with 50+ SMBs are shown"}
activity_by_settlements
```

@@

```{r fig-6-activity-by-settlements_svr, fig.cap = "Fig. 6. Count of SMBs in settlements of Sverdlovsk region with dominant activity type. The counts are represented with circle size, and the most popular activity group in the settlement is displayed by color. All settlements regardless of the counts are shown"}
activity_by_settlements_svr
```

@@

```{r tab-3-corr-by-year}
knitr::kable(
  corr_by_year,
  digits = 2, 
  col.names = c("Year", "$\\rho_{Spearman}$, all activity groups", "$\\rho_{Spearman}$, excluding groups O, P, U"),
  caption = "Table 3. The correlation between the count of SMBs and total count of businesses by year")
```

@@

```{r fig-9-corr-by-region, fig.cap = "Fig. 9. Distribution of regions by the correlation coefficient between the SMBs counts and total businesses counts"}
corr_by_region_plot
```

@@

```{r tab-4-corr_by_group}
knitr::kable(
  corr_by_group,
  digits = 2,
  col.names = c("Activity group", "$\\rho_{Spearman}$"),
  caption = "Table 4. The correlation between the count of SMBs and total count of businesses by activity group")
```

>>>>

**Technology of Making a Geo-Referenced Dataset about Small and Medium-Sized Businesses in Russia Based on the Federal Tax Service's Open Data**

@@

Pavel O. Syomin: ntsp\@ya.ru, ORCID 0000-0002-4015-9206

@@

```{r tab-1-sizes-funnel}
bytes_in_mb <- 2 ** 20
sizes_funnel <-  sizes_funnel / bytes_in_mb
knitr::kable(
  sizes_funnel,
  digits = 0,
  format.args = list(scientific = FALSE),
  col.names = c("SMB Registry", "Revenue+Expediture", "Employees", "Total"),
  caption = "Table 1. Change in the data volume during program execution (in megabytes). Rows are stages, columns are source datasets and totals")
```

@@

```{r fig-3-regions-agri-forest, fig.cap = "Fig. 3. Regional distribution of SMBs which main activity is agriculture or forestry, in 2021. Color represents the min-max scaled value"}
regions_plot_agri_forestry
```

@@

```{r fig-3-regions-wheat-potato, fig.cap = "Fig. 4. Regional distribution of SMBs which main activity is growing of wheat or potato, in 2021. Color represents the min-max scaled value, gray is no data"}
regions_plot_wheat_potato
```

@@

```{r fig-5-activity-by-settlements-russia, fig.cap = "Fig. 5. Count of SMBs in some Russian settlements with dominant activity type, in 2021. The counts are represented by circle size, and the most popular activity group in the settlement is displayed by color. Only settlements with 50+ SMBs are shown"}
activity_by_settlements
```

@@

```{r fig-6-activity-by-settlements_svr, fig.cap = "Fig. 6. Count of SMBs in settlements of Sverdlovsk region with dominant activity type, in 2021. The counts are represented by circle size, and the most popular activity group in the settlement is displayed by color. All settlements regardless of the counts are shown"}
activity_by_settlements_svr
```

@@

```{r tab-3-corr-by-year}
knitr::kable(
  corr_by_year,
  digits = 2, 
  col.names = c("Year", "$\\rho_{Spearman}$, all activity groups", "$\\rho_{Spearman}$, excluding groups O, P, U"),
  caption = "Table 3. The correlation between the count of SMB organizations and total count of commercial organizations by year")
```

@@

```{r fig-9-corr-by-region, fig.cap = "Fig. 9. Distribution of regions by the correlation coefficient between the SMB organizations counts and total commercial organizations counts"}
corr_by_region_plot
```

@@

```{r tab-4-corr_by_group}
knitr::kable(
  corr_by_group,
  digits = 2,
  col.names = c("Activity group", "$\\rho_{Spearman}$"),
  caption = "Table 4. The correlation between the count of SMB organizations and total count of commercial organizations by activity group")
```
